Active Learning for SAT Solver Benchmarking {\large (extended and revised version)}

### 2024-05-24 paper_jar/paper.tex
title

\title[Active Learning for SAT Solver Benchmarking]{Active Learning for SAT Solver Benchmarking} % short and long title

@@

This article is an extended and refined version of our conference paper with the same title, ``Active Learning for SAT Solver Benchmarking''~\cite{fuchs2023active}.
In particular, we significantly extended the analysis of runtime-prediction approaches, which led to our choice of a solver runtime model for use in benchmark instance selection (cf.~Section~\ref{sec:exdesign:disc-pred}).
Furthermore, we expanded the evaluation of which benchmark instances are selected by our approach (cf.~Section~\ref{sec:eval:instance}).
% TODO: before submission, we should check which other changes we made and list them here accordingly

>>>>

\title[Active Learning for SAT Solver Benchmarking]{Active Learning for SAT Solver Benchmarking {\large (extended and revised version)}} % short and long title

@@

This article is an extended and refined version of our conference paper with the title ``Active Learning for SAT Solver Benchmarking''~\cite{fuchs2023active}.
In particular, we significantly extended the analysis of runtime-prediction approaches, which led to our choice of a solver runtime model for use in benchmark instance selection (cf.~Section~\ref{sec:exdesign:disc-pred}).
Furthermore, we expanded the evaluation of which benchmark instances are selected by our approach (cf.~Section~\ref{sec:eval:instance}).
% TODO: before submission, we should check which other changes we made and list them here accordingly
